comgen-outline

### 2017-12-18 paper/comgen-paper.Rmd
revert to using prevalence as the term

Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **feature-probability**.
The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
The properties also vary (e.g., having fur, causing jitters, typing). 
Yet the mathematical description of the inductive inference is always given by the conditional feature-probability $h$.

How does one acquire such an inductive belief?
One can observe instances of the category $k$ and note how many of them have $f$.
These observations can support prediction to new instances by integrating them with one's prior expectations about the property [cf., @Gelman2003; @Keil1992].
For example, if you observe creatures that \textsc{have two legs}, you might infer that all creatures of that category have two legs.
Observing new creatures with \textsc{broken wings}, however, leads to a much weaker prediction about other instances of the category having the property [@Nisbett1983].
This kind of background knowledge can be represented formally as a probability distribution over the feature-probabilities $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$

@@

<!-- Here, $P(d \mid h)$ is the observer's generative model of the observed data.  -->
<!-- It is conditional on $h$ because the probability of various direct observations depends upon the feature-probability that the observer assumes.  -->
<!-- Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
<!-- How do we acquire these generalizations? -->
<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations. -->
<!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000]. -->
<!-- From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007]. -->
<!-- Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).  -->
<!-- This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances. -->

@@

<!-- The observer goes around the world, encountering dogs and taking note of how many bark. -->
<!-- This could be represented as a number of positive examples $d$ out of a number of total examples $n$.  -->
<!-- With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.  -->
<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the feature-probability of barking among dogs. -->
<!-- This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$.  -->
<!-- Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule: -->

@@

Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity will be at the core of a semantic theory of the language of generalization.
To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean value.
One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
A threshold semantics for the language of generlizations would then apply to the *feature-probability* $h$:
\begin{equation}
\denote{generalization}(h, \theta) = \{h>\theta\}
\label{eq:semantics}
\end{equation}
Various attempts of this kind have been made before [e.g., @Cohen1999].
We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $h$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.  
$h$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief (due to background knowledge, see above).

<!-- We emphasize that this account is based on a probability $h$. -->
<!-- The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the feature-probability $h$.^[ -->
<!--   There has also been substantial discussion of *cue validity* , which we come back to below. -->
<!-- ] -->
<!-- Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself.  -->
<!-- Probability is a measure of belief.  -->

@@

Equation \ref{eq:L0} ($Interpret$) is a literal interpretation model, that updates its beliefs about the feature-probability $h$ according to the truth-functional meaning of the utterance $u$. 
Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.

@@

Given the above minimal model of literal interpretation, how do we decide when a statement conveying a generalization is true or not?
We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey sufficient information to warrant the cost of producition? 
We formalize this by considering how well the generalization would convey the feature-probability $h$ to the $Interpret$ model (Eq. \ref{eq:L0})^[A more general version of this model can relax the assumption that the endorsement model has access to a specific feature-probability $h'$ that it wants to communicate.
Rather, the endorser may have a distribution over $h'$ for the category $k$, corresponding to the endorser's uncertain beliefs about the feature-probability. 
In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorser's belief distribution:
$Endorse(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} Interpret(h, \theta \mid u)} \diff \theta )}$
For the empirical case studies described below, these two versions of the model make almost identical predictions.
].

@@

Our endorsement model (Eq. \ref{eq:S1}) provides a straight-forward mapping from a *referent-category feature-probability* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"). 
It does this assuming a threshold semantics based on probability but does not require specifying the threshold *a priori* (note that there is not $\theta$ is Eq. \ref{eq:S1}).
This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016], where there is only a single level of recursion and the space of possible utterances is maximally constrained.

@@

<!-- Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function. -->
<!-- Because we are interested in determining whether or not *feature-probability* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category feature-probability* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$). -->

@@

The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the feature-probability communicated in the category under discussion $h'$ in Eq. \ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about feature-probabilities $P(h)$ (Eq. \ref{eq:L0}).
We simulate how these two factors change both literal interpretation and endorsement using hypothetical values based on intuition about classic examples from the literature on generic language.

<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq. \ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq. \ref{eq:L0}), as well as the referent-category feature-probability $h$ (Eq. \ref{eq:S1}). -->
<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent). -->
<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}). -->

@@

```{r cache = F}
fig.sims.fixed.thresholds <- ggplot(sims.fixed.thresholds, aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.3)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability") +
    ylab("") +
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~threshold, scales = 'free')+
    theme(strip.text.y = element_blank(), axis.title.x = element_text(hjust = 1))
```

@@

```{r fig.width = 9, eval = F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")

@@

# s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
#   #geom_jitter(width = 0.1, shape = 21, size = 5)+
#   #ylab("Human endorsement probability")+
#   #xlab("Frequency of target")+
#   geom_label_repel(data = s1.simulations.relabeled, 
#                    aes( label = example, fill = example),
#                        color = 'white',
#     box.padding = unit(0.0, "lines"),
#     #point.padding = unit(1e-06, "lines"),
#     segment.color = 'grey37')+
#   scale_fill_solarized()+
#   scale_x_continuous(limits = c(0, 1), 
#                      breaks = c(0, 0.5, 1))+
#   scale_y_continuous(limits = c(-0.01, 1.01), 
#                      breaks = c(0, 1),
#                      labels = c("False", "True"))+
#   coord_fixed(ratio = 1)+
#   guides(fill = F)+
#   ylab("Endorsement model prediction")+
#   xlab("Hypothesized feature-probability")

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
  geom_col(color = 'black')+
  # geom_label_repel(data = s1.simulations.relabeled, 
  #                  aes( label = example, fill = example),
  #                      color = 'white',
  #   box.padding = unit(0.0, "lines"),
  #   #point.padding = unit(1e-06, "lines"),
  #   segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1),
                     labels = c("False", "True"))+
  #coord_fixed(ratio = 1)+
  coord_flip()+
  facet_grid(example~.)+
  guides(fill = F)+
  ylab("Endorsement")+xlab("Referent feature-probability")+
  theme(strip.text.y = element_text(angle = 0, hjust = 0)
        #axis.title.x = element_text(hjust = 0)
        #axis.title.y = element_text(vjust = 0)
        )
  #ylab("Endorsement model prediction")+
  #xlab("Hypothesized feature-probability")
```

```{r simulations, fig.cap = "Computational model behavior. A: Prior distributions over feature-probabilities for 6 example generalizations. B: Different fixed thresholds (columns) give rise to different posterior interpretations. C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors. D: Endorsement model predictions, assuming a particular referent feature-probability. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("Feature-probability priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

@@

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability h") +
    ylab("Scaled prior probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability h") +
    ylab("Scaled prior probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))

@@

Figure\ \@ref(fig:simulations) (left; filled colors) shows six prior distributions over feature-probabilities, representing the relevant background knowledge about each property.
These distributions can be thought of as distributions over categories, displaying only the feature-probability for the property in question.
For example, many different kinds of animals *do not bark*; thus, there is substantial probability mass near 0 for the prior distribution over the feature-probability of \textsc{barks} (top left; solid pink distribution). 
In addition, among the categories that do have instances that bark (e.g., \textsc{dogs}, \textsc{seals}, ...), the probability is quite high that an instance will bark; thus, the feature-probability distribution has substantial mass at relatively high values, with the maximum probability-density occuring around 0.9 (though with quite a bit of uncertainty around this value).

The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}. 
This gives the literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") given the background knowledge about the property.
For instance, the interpretation of a generalization about the property \textsc{barks} is that the feature-probability is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
This would correspond to a rather strong interpretation (i.e., "Almost all feps bark").
This is not the case for the \textsc{lays eggs} distribution (a la "Feps lay eggs"; bottom left, green). 
Given the background knowledge about that property----not that many animals lay eggs, and among those for which the feature is present, the probability is about 0.5 (because it's only present in the females)----the interpretation is much more conservative: "About half of feps lay eggs".
The model can even derive very weak interpretations, as is shown in the \textsc{carries malaria} distribution (bottom right, purple).
Again, the literal interpretation depends upon the background knowledge in a deep way.

>>>>

Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find certain people typing.
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$.
This prediction can be described by a conditional probability: $h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$, which we will refer to as the **prevalence**.
The targets of our predictions can vary widely: They may be objects (a dog), events (a coffee drink), or more fine grained types (a person on a given day).
The properties also vary (e.g., having fur, causing jitters, typing). 
Yet the mathematical description of the inductive inference is always given by the prevalence $h$.

How does one acquire such an inductive belief?
One can observe instances of the category $k$ and note how many of them have $f$.
These observations can support prediction to new instances by integrating them with one's prior expectations about the property [cf., @Gelman2003; @Keil1992].
For example, if you observe creatures that \textsc{have two legs}, you might infer that all creatures of that category have two legs.
Observing new creatures with \textsc{broken wings}, however, leads to a much weaker prediction about other instances of the category having the property [@Nisbett1983].
This kind of background knowledge can be represented formally as a probability distribution over the prevalence $h$: $P(h)$ [@Kemp2008], and observational data $d$ can update one's beliefs via Bayes' Rule: $P(h \mid d) \propto P(d \mid h) \cdot P(h)$

@@

<!-- Here, $P(d \mid h)$ is the observer's generative model of the observed data.  -->
<!-- It is conditional on $h$ because the probability of various direct observations depends upon the prevalence that the observer assumes.  -->
<!-- Generalization from observational evidence is limited, however, in its capacity to describe how the mind builds complex theories of the world or how culture accumulates across generations. -->
<!-- How do we acquire these generalizations? -->
<!-- For abstract, generalizable knowledge to remain in a culture, it must be faithfully transmitted between individuals and across generations [@Tomasello1999], and language provides simple ways to communicate generalizations. -->
<!-- The human capacity to generalize from observations, deriving $h$ from example $x$s, has been studied extensively in cognitive and developmental psychology [@Nisbett1983; @Baldwin1993; @Heit2000]. -->
<!-- From a very young age, children draw strong inferences about nonobvious object properties from just a few examples [@Baldwin1993; @Gopnik2000;  @XuTenenbaum2007]. -->
<!-- Such inductive generalization can be described by the Bayesian probability calculus: An observer's initial beliefs or state of knowledge---called a prior belief distribution---is updated through experience (i.e., after making observations) and becomes a posterior belief distribution (what they belief *a posteriori*).  -->
<!-- This posterior distribution becomes the observer's prior for the next observation she makes: it thus informs her predictions about unobserved instances. -->

@@

<!-- The observer goes around the world, encountering dogs and taking note of how many bark. -->
<!-- This could be represented as a number of positive examples $d$ out of a number of total examples $n$.  -->
<!-- With the weak assumption that the dogs she has observed were all independent and identically-distributed (*i.i.d.*) random samples from the category of dogs, the likelihood of her observations are given by the Binomial distribution.  -->
<!-- That is, $d \sim  \text{Binomial}(n, h)$, where $d$ is the number of dogs she has seen that bark, $n$ is the total number of dogs she has seen, and $h$ is the prevalence of barking among dogs. -->
<!-- This is called a likelihood function: It determines how well a given value of $h$ predicts the observed $d$.  -->
<!-- Given a formal description of the learner's state of knowledge before any observations $P(h)$ and the learner's assumptions about how the data she observed were generated (e.g., the *i.i.d.* assumption), what a learner should believe after having seen the data is proportional to the product of these two terms, as given by Bayes' Rule: -->

@@

Generalization from observations can be described as a predictive probability; it is intuitive then to posit that same quantity will be at the core of a semantic theory of the language of generalization.
To connect to the semantic tools of *truth values* [@Montague1973], we must relate the scalar quantity of probability to a Boolean value.
One simple way is with a *threshold semantics*: An utterance is true if the relevant quantity is above a threshold.
A threshold semantics for the language of generlizations would then apply to the *prevalence* $h$:
\begin{equation}
\denote{generalization}(h, \theta) = \{h>\theta\}
\label{eq:semantics}
\end{equation}
Various attempts of this kind have been made before [e.g., @Cohen1999].
We distinguish our proposal from previous ones by emphasizing the cognitive underpinnings of $h$, as well as the formalization into a model that makes precise, quantitative predictions about human endorsements.  
$h$ describes a latent belief and should not be confused with *frequency*, which can inform a belief but is not itself the belief (due to background knowledge, see above).

<!-- We emphasize that this account is based on a probability $h$. -->
<!-- The literature on generic language has often focused on *prevalence*---either the actual or believed proportion of members of a category with the property---which we distinguish from the prevalence $h$.^[ -->
<!--   There has also been substantial discussion of *cue validity* , which we come back to below. -->
<!-- ] -->
<!-- Prevalence, an ostensibly observable quantity, can inform a person's beliefs (e.g., via Bayesian belief updating) but it is not the belief itself.  -->
<!-- Probability is a measure of belief.  -->

@@

Equation \ref{eq:L0} ($Interpret$) is a literal interpretation model, that updates its beliefs about the prevalence $h$ according to the truth-functional meaning of the utterance $u$. 
Formally, the truth-functional meaning is represented by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$ that returns probabilities proportional to $1$ when the utterance is true (i.e., when $h > \theta$) and $0$ otherwise.

@@

Given the above minimal model of literal interpretation, how do we decide when a statement conveying a generalization is true or not?
We consider the notion of felicity or endorsement from the information-theoretic perspective: Would a generalization convey sufficient information to warrant the cost of producition? 
We formalize this by considering how well the generalization would convey the prevalence $h$ to the $Interpret$ model (Eq. \ref{eq:L0})^[A more general version of this model can relax the assumption that the endorsement model has access to a specific prevalence $h'$ that it wants to communicate.
Rather, the endorser may have a distribution over $h'$ for the category $k$, corresponding to the endorser's uncertain beliefs about the prevalence. 
In this situation, we would define the endorsement model decision to be with respect to the expected value of the informativity, which integrates over the endorser's belief distribution:
$Endorse(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} Interpret(h, \theta \mid u)} \diff \theta )}$
For the empirical case studies described below, these two versions of the model make almost identical predictions.
].

@@

Our endorsement model (Eq. \ref{eq:S1}) provides a straight-forward mapping from a *referent-category prevalence* $h'$  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) to an endorsement probability for the corresponding generalization (e.g., "Robins lay eggs"). 
It does this assuming a threshold semantics based on probability (prevalence) but does not require specifying the threshold *a priori* (note that there is not $\theta$ is Eq. \ref{eq:S1}).
This model can be seen as a special case of a Rational Speech Act model [@Frank2012; @Goodman2016], where there is only a single level of recursion and the space of possible utterances is maximally constrained.

@@

<!-- Following the Rational Speech Act framework, the speaker (called $E$ for endorsement) is assumed to be an approximately rational Bayesian agent who produces utterances according to their utility $U$ with rationality governed by parameter $\lambda$, which acts as a soft-max function. -->
<!-- Because we are interested in determining whether or not *prevalence* alone is sufficient to formalize generalizations in language, we define the endorsement utility as a function of only the utterance (say the generalization or stay silent) and the *referent-category prevalence* $h'$ (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$). -->

@@

The endorsement model defined in the previous section explicitly predicts that the variability in endorsements for generalizations in language can be explained by two factors: (i) the prevalence communicated in the category under discussion $h'$ in Eq. \ref{eq:S1} (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$) and (ii) the background knowledge about prevalences $P(h)$ (Eq. \ref{eq:L0}).
We simulate how these two factors change both literal interpretation and endorsement using hypothetical values based on intuition about classic examples from the literature on generic language.

<!-- depends upon the probability that utterance vs. silence accurate conveys to a naive listener a. -->
<!-- This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq. \ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the prevalence in question: $P(h)$ (Eq. \ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq. \ref{eq:S1}). -->
<!-- Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent). -->
<!-- For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}). -->

@@

```{r cache = F}
fig.sims.fixed.thresholds <- ggplot(sims.fixed.thresholds, aes(x = state, fill = PriorShape, color = PriorShape))+
    geom_density(aes(y = ..scaled..), size = 0.6, alpha = 0.3)+
    theme_few() +
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence of the feature in a category") +
    ylab("") +
    scale_color_solarized()+
    scale_fill_solarized()+
    facet_grid(PriorShape~threshold, scales = 'free')+
    theme(strip.text.y = element_blank(), axis.title.x = element_text(hjust = 1))
```

@@

```{r fig.width = 9, eval = F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,0,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")

@@

# s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement))+
#   #geom_jitter(width = 0.1, shape = 21, size = 5)+
#   #ylab("Human endorsement probability")+
#   #xlab("Frequency of target")+
#   geom_label_repel(data = s1.simulations.relabeled, 
#                    aes( label = example, fill = example),
#                        color = 'white',
#     box.padding = unit(0.0, "lines"),
#     #point.padding = unit(1e-06, "lines"),
#     segment.color = 'grey37')+
#   scale_fill_solarized()+
#   scale_x_continuous(limits = c(0, 1), 
#                      breaks = c(0, 0.5, 1))+
#   scale_y_continuous(limits = c(-0.01, 1.01), 
#                      breaks = c(0, 1),
#                      labels = c("False", "True"))+
#   coord_fixed(ratio = 1)+
#   guides(fill = F)+
#   ylab("Endorsement model prediction")+
#   xlab("Hypothesized prevalence")

s1.simulations.scatter <- ggplot(s1.simulations.relabeled, aes( x = featureProb, y = endorsement, fill = example))+
  geom_col(color = 'black')+
  # geom_label_repel(data = s1.simulations.relabeled, 
  #                  aes( label = example, fill = example),
  #                      color = 'white',
  #   box.padding = unit(0.0, "lines"),
  #   #point.padding = unit(1e-06, "lines"),
  #   segment.color = 'grey37')+
  scale_fill_solarized()+
  scale_x_continuous(limits = c(0, 1), 
                     breaks = c(0, 1))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 1),
                     labels = c("False", "True"))+
  #coord_fixed(ratio = 1)+
  coord_flip()+
  facet_grid(example~.)+
  guides(fill = F)+
  ylab("Endorsement")+xlab("Referent prevalence")+
  theme(strip.text.y = element_text(angle = 0, hjust = 0)
        #axis.title.x = element_text(hjust = 0)
        #axis.title.y = element_text(vjust = 0)
        )
  #ylab("Endorsement model prediction")+
  #xlab("Hypothesized prevalence")
```

```{r simulations, fig.cap = "Computational model behavior. A: Prior distributions over the prevalence of a feature in a category for 6 example features B: Different fixed thresholds (columns) give rise to different posterior interpretations. C: The interpreter model averages over all thresholds, producing posterior distributions that strongly depend upon the priors. D: Endorsement model predictions, assuming a particular referent-prevalence. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 12, cache=F}
p1 <- fig.sims.priors +
  theme(plot.margin = unit(c(18,2,6,6), "pt")) #+ ggtitle("prevalence priors")
p2 <- fig.sims.fixed.thresholds +
  theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab("")
p3 <- fig.sims.uncertain.threshold+
  theme(plot.margin = unit(c(18,2,6,6), "pt"))+ 
    theme(strip.text.y = element_blank())#+ ggtitle("Interpreter model posterior")
p4 <- s1.simulations.scatter + theme(plot.margin = unit(c(18,0,6,6), "pt"))

@@

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence of feature in a category") +
    ylab("Scaled probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))

l0.simulations.distributions <- ggplot(all.simulations.refactored, aes(x = value, #y = prob, 
                color = PriorShape, fill = PriorShape, group = Distribution, alpha = Distribution, linetype = Distribution))+
    geom_density(aes(y = ..scaled..),
                 size = 0.6,  adjust = 1.5)+
    theme_few() +
    scale_color_solarized()+
    scale_fill_solarized()+
    scale_alpha_manual(values = c(0.7, 0.3))+
    scale_linetype_manual(values = c(1, 3))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence of feature in a category") +
    ylab("Scaled probability density") +
  facet_wrap(~PriorShape, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0),
          legend.position = c(0.92, 0.35))

@@

Figure\ \@ref(fig:simulations) (left; filled colors) shows six prior distributions over feature-probabilities, representing the relevant background knowledge about each property.
These distributions can be thought of as distributions over categories, displaying only the prevalence for the property in question.
For example, many different kinds of animals *do not bark*; thus, there is substantial probability mass near 0 for the prior distribution over the prevalence of \textsc{barks} (top left; solid pink distribution). 
In addition, among the categories that do have instances that bark (e.g., \textsc{dogs}, \textsc{seals}, ...), the probability is quite high that an instance will bark; thus, the prevalence distribution has substantial mass at relatively high values, with the maximum probability-density occuring around 0.9 (though with quite a bit of uncertainty around this value).

The lighter distribution is the interpretation distribution given by Eq. \ref{eq:L0}. 
This gives the literal interpretation of a generalization about a previously unknown category (e.g., "Feps bark.") given the background knowledge about the property.
For instance, the interpretation of a generalization about the property \textsc{barks} is that the prevalence is quite high, near 1 with some uncertainty (top left; lighter pink distribution).
This would correspond to a rather strong interpretation (i.e., "Almost all feps bark").
This is not the case for the \textsc{lays eggs} distribution (a la "Feps lay eggs"; bottom left, green). 
Given the background knowledge about that property----not that many animals lay eggs, and among those for which the feature is present, the probability is about 0.5 (because it's only present in the females)----the interpretation is much more conservative: "About half of feps lay eggs".
The model can even derive very weak interpretations, as is shown in the \textsc{carries malaria} distribution (bottom right, purple).
Again, the literal interpretation depends upon the background knowledge in a deep way.
